% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Introduction}\label{chap:introduction}

% TODO: does https://arxiv.org/pdf/2310.03256 say cable is not faster than streaming?

The fact that online streaming tends to be slower than cable TV is likely something most people have already 
experienced first-hand.
Live sports events, music shows, or news broadcasts arrive an order of seconds later when streamed compared
to using traditional cable connections. % TODO: citation needed
Despite this delay not necessarily being a deal-breaker, designing networks that 
tighten the gap between cable and streaming is still worthwhile.
With very optimized and fast networks already in place, we are at a point where providing faster information
delivery is highly non-trivial.
To do that, we have even gone as far as developing entirely new standards, such as QUIC\@. 
Those new standards aim to improve the shortcomings of some of the most fundamental protocols of the Internet, which have been around for more than 40 years, one of them being TCP\@. 


Besides introducing new protocols, one could also look at existing setups and figure out how to trade some generality
for a smaller delay when handling data.
The ISO/OSI model, which is a foundational concept in networking, provides ``a common basis for the coordination 
of standards development for the purpose of systems interconnection''~\parencite{iso-osi-standard}.
As one can imagine, such a ``common basis'', even though convenient for large-scale systems, can cause unnecessary
overhead.
In some cases, additional speed-ups can be achieved by using more application-specific approaches.
This thesis will consider one such case and explore the possibilities of avoiding or delaying specific processing
steps of the ISO/OSI model to increase the overall speed of a network relay.

\input{chapters/01_subchapters/01_research_question}
\input{chapters/01_subchapters/02_scope}
\input{chapters/01_subchapters/03_structure_of_thesis}


% % TODO: remove %
% \section{Citation Examples}
% Citation~\parencite{rfc-9000}.
% Citation~\parencite{iso-osi-standard}.
% Citation~\parencite{draft-moqtransport}.
% Citation~\parencite{article-quic-usage}.
% Citation~\parencite{internet-quic-usage}.
% Citation~\parencite{facebook-quic-usage}.
% Citation~\parencite{google-quic-usage}.
% Citation~\parencite{quic-nic-offload}.
% Citation~\parencite{quic-explained}.
% Citation~\parencite{equic-gateway}.
% Citation~\parencite{media-streaming-prio-drop}.
% Citation~\parencite{quic-nic-offload-patent}.
% Citation~\parencite{kernel-bypass-msc-thesis}.
% Citation~\parencite{quic-go-repo}.
% Citation~\parencite{quic-go-prio-packs-repo}.
% Citation~\parencite{adaptive-moq-repo}.
% Citation~\parencite{priority-moqtransport-repo}.
% Citation~\parencite{fast-relays-thesis-repo}.
% Citation~\parencite{ebpf-verifier}.